Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

# Set locale
tmp <- Sys.setlocale(locale="UTF-8")

# Nice theme
# theme_set(theme_bw(26))

# Nice default themes
# https://github.com/cttobin/ggthemr#palettes
#ggthemr('fresh', text_size = 20)
# ggthemr('greyscale', text_size = 20)
#ggthemr('light', text_size = 20)
# ggthemr('pale', text_size = 20)
#ggthemr_reset() # Reset theme
```

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count per capita (n)") +
       #scale_color_stata() +
       #scale_color_manual(values = city.colors[as.character(levels(dfm$publication_place))]) +
       scale_color_manual(values = city.colors[match(unique(dfm$publication_place), names(city.colors))]) +              
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) 
       #ggtitle("Title count per capita") +
       # ggtitle("Figure 11") +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

>>>>

# Set locale
tmp <- Sys.setlocale(locale="UTF-8") 
```

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count per capita (n)") +
       #scale_color_stata() +
       #scale_color_manual(values = city.colors[as.character(levels(dfm$publication_place))]) +
       scale_color_manual(values = city.colors[match(unique(dfm$publication_place), names(city.colors))]) +              
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +
       #ggtitle("Title count per capita") +
       # ggtitle("Figure 11") +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)
